### 2016-01-15 paper.tex
Clean up CFT kinematics description as suggested by @wosnik

As a cross-flow turbine, the RM2 blades experience large variations in angles of
attack as they rotate about their axis (``cross-flow turbine'' means the axis of
rotation is perpendicular to flow direction---either vertically or
horizontally). These variations become larger at lower tip speed ratio
\begin{equation}
    \lambda=\frac{\omega R}{U_\infty},
\end{equation}
where $\omega$ and $R$ are the rotor angular velocity and radius
\cite{Para2002}. Typically, the maximum angles of attack are sufficiently large
that the blades operate under dynamic stall, which is a complex unsteady process
and deviates significantly from static foil behavior, during part of the
rotation. Furthermore, the higher the solidity of a cross-flow turbine, the
lower the optimal tip-speed ratio at which it operates. Marine Hydrokinetic
(MHK) cross-flow turbines typically have higher solidity than cross-flow wind
turbines (VAWT), and hence operate at lower tip-speed ratios. Since MHK turbines
operate in a higher density fluid, unsteady dynamic effects related to the
blades' pitching motion and flow curvature also become more important when
compared to wind turbines.

>>>>

As a consequence of the inherently unsteady nature of the cross-flow rotor, the
RM2 blades experience large variations in angles of attack as they rotate about
their axis (``cross-flow'' means the axis of rotation is perpendicular to flow
direction). These variations become larger at lower tip speed ratio
\begin{equation}
    \lambda=\frac{\omega R}{U_\infty},
\end{equation}
where $\omega$ and $R$ are the rotor angular velocity and radius
\cite{Para2002}. Typically, the maximum angles of attack are sufficiently large
that the blades operate under dynamic stall, which is a complex unsteady process
and deviates significantly from static foil behavior, during part of the
rotation. Furthermore, the higher the solidity of a cross-flow turbine, the
lower the optimal tip-speed ratio at which it operates. Marine Hydrokinetic
(MHK) cross-flow turbines typically have higher solidity than cross-flow wind
turbines (VAWT), and hence operate at lower tip-speed ratios. Since MHK turbines
operate in a higher density fluid, unsteady dynamic effects related to the
blades' pitching motion and flow curvature also become more important when
compared to wind turbines.
